The development of infants' responses to mispronunciations: A Meta-Analysis

### 2020-07-01 VonHolzenBergmann_MPMetaAnalysis.Rmd
Dev Psych start of revision (1st round)

In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g. cat-hat). This meta-analysis examines on the latter, focusing how infants apply the relevant phonological categories of their native language, aggregating twenty years' worth of studies using the mispronunciation sensitivity paradigm. The original study of @Swingley2000 presented American-English learning 18- to 23-month-olds with pairs of images of words they were very likely to know (e.g. a baby and a dog) and their eye movements to each image were recorded. Infants either heard the correct label (e.g. "baby") or a mispronounced label (e.g. "vaby") for one of the images. Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looks to the target image than mispronounced labels. @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified. As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired and applied to lexical representations. The time is thus ripe to aggregate all publicly available evidence using a meta-analysis. In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies (see @MB1 for a notable exception).

An *increase* in mispronunciation sensitivity with age is predicted by a maturation from holistic to more detailed phono-lexical representations and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010]. The first words that infants learn are often not similar sounding [e.g. mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary. According to PRIMIR [@Curtin2007; @Werker2005] infants's initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task. This argument is supported by the results of @Mani2010kepstups, who found that 12-month-old infants with a larger vocabulary showed a greater sensitivity to vowel mispronunciations than infants with a smaller vocabulary.

@@

There are no theoretical accounts that would predict *decreased* mispronunciation sensitivity, but at least one study has found a decrease in sensitivity to small mispronunciations. Here, 18- but not 24-month-old infants showed sensitivity to more subtle mispronunciations that differed from the correct pronunciation by 1 phonological feature [@Mani2011]. When faced with large and salient mispronunciations, sensitivity to small 1-feature mispronunciations may be obscured, especially if infants show graded sensitivity to different degrees of mispronunciations (see below), as @Mani2011 found with 24- but not 18-month-olds in their study.

To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size. But, this may not account for all variability found in the literature. Many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that is either familiar or completely novel. We thus include an analysis of the features of the task to shed further light on early phono-lexical representations and their maturation.

These research questions and experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail. The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment. In a particularly demanding task, such as when the target and distractor image share the same onset (e.g. doggie and doll), infants' ability to access the phonological detail of familiar words may be restricted [@Swingley1999]. If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies. Note, however, that those studies reporting change [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010] or no change [@Swingley2000; @Bailey2002; @Zesiger2012] all presented the same task across ages.

The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations. Some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e. 1-feature, 2-features, 3-features, etc.), finding graded sensitivity to both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] feature changes. This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity [@Bailey2005]

The COHORT model [@Marslen-Wilson1989] describes lexical access in one direction, with the importance of each phoneme decreasing as its position comes later in the word. In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations. To evaluate these competing theories, studies often manipulate the *mispronunciation position*, whether onset, medial, or coda, in the word.

@@

A second set of questions is whether the context modulates infants' responses to mispronunciations. In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a vowel mispronunciation of the target word "doggie", the image of a dog would be paired with a distractor image that shares onset overlap, such as "doll". This ensures that infants can not use the onset of the word to differentiate between the target and distractor images [@Swingley1999]. Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.

@@

Mispronunciation sensitivity studies typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper. Over half of the records (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score. The Difference Score is one value, which is then compared with a chance value of 0. In contrast, Pre vs. Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` records), directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g. t-test, ANOVA). This requires two values, one for the pre-naming phase and one for the post-naming phase. The remaining records used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` records), which compares the post-naming PTL score with a chance value of 50%. Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%). Standardized effect sizes based on mean differences, as calculated here, preserve the sign. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.

@@

In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounced words (`r mod_test(rma_MP_age)`). The lack of a significant modulation together with the small estimates for age (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there might be no relationship between age and target looks in response to a correctly pronounced or mispronounced label.

@@

```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=7, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age. Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) by participant age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  ggtitle("a. Object Recognition")+
  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
  #geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_manual(values=cbPalette)+
  xlim(6, 31) +
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
  ggtitle("b. Mispronunciation Sensitivity")+
  geom_point(aes(size = weight),show.legend=FALSE, alpha = .3) + 
  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
  #geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
  scale_colour_manual(values=cbPalette)+
  xlim(6, 31) +
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

vocab_year <- ggplot(d.v,aes(x=Year, fill = relationship)) + 
  apatheme+
  geom_histogram(alpha = 0.5, bins = 20) +
    scale_fill_manual(values=cbPalette)+
     theme(legend.position = "bottom",
           legend.title = element_blank())

@@

#   
# 
# vocab_data1 <- dat.v %>%
#   group_by(year, relationship, tested) %>%
#   summarize(count = n())
# 
# vocab_data1 <- as.data.frame(vocab_data1)
# vocab_data1$count <- ifelse(vocab_data1$tested == "no", 0, vocab_data1$count)
# vocab_data1$year <- as.numeric(vocab_data1$year)
# 
# vocab_data1$relationship <- ifelse(vocab_data1$relationship == "no_vocab", "None",
#                                    ifelse(vocab_data1$relationship == "positive", "Predicts",
#                                           "No Relationship"))
# vocab_data1$relationship <- factor(vocab_data1$relationship, levels = c("Predicts", "No Relationship", "None"))
# 
# 
# p <- ggplot(vocab_data1, aes(year, count, color = relationship)) + 
#   geom_line() + 
#   geom_point()+
#   scale_y_continuous(breaks = c(0, 1, 2, 3, 4), limits = c(0,4))+
#   scale_colour_manual(values=cbPalette)+
#   apatheme +
#   theme(legend.title = element_blank(),
#         legend.position = "bottom")
# p
# 
#   jpeg(filename = "figures/Vocab_findings.jpg", 
#        width = 500, height = 300, units = "px")
# 
#   p
#   
#   dev.off()
#  
```

@@

If infants' word recognition skills are generally thought to improve with age and vocabulary size, research questions that tap more complex processes may be more likely to be investigated in older infants. In this section, we consider each moderator individually and investigate its influence on mispronunciation sensitivity. For most moderators (except mispronunciation size), we combine the correct and mispronounced datasets and include the moderator of condition, to study mispronunciation sensitivity as opposed to object recognition. To better understand the impact of these moderators on developmental change, we include age as subsequent moderator. Results of the moderator tests as well as the individual effects for each moderator interaction are reported in Table 2. All moderator tests were significant and subsequent significant interactions of critical terms are interpreted. Finally, we analyze the relationship between infant age and the moderator condition they were tested in using Fisher's exact test, which is more appropriate for small sample sizes [@Fisher1922]. This evaluates the independence of infants' age group (divided into quartiles unless otherwise specified) and assignment to each type of condition in a particular moderator.

@@

To assess whether the size of the mispronunciation tested, as measured by the number of features changed, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` records for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations. Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an graded impact on mispronunciation sensitivity [@White2008; @Mani2011] and this moderator was coded as a continuous variable. We did not include records for which the numer of features changed was not specified or consistent within a record (e.g., both 1- and 2-feature changes within one mispronunciation record).

@@

p.MS <- ggplot(dat.f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_violin() + 
  geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Hedges' g")

@@

ms.age <- ggplot(dat.f, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

```{r PlotMispPosit, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions. Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

ms.agg <- ggplot(dat.cm, aes(location_label, Misp_sensitivity, fill = location_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

@@

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = location_label)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

```{r PlotMispType, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations. Panel b: Effect sizes for mispronunciation sensitivity (correct - mispronunciations) for consonant and vowel mispronunciations by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_manual(values=cbPalette)+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_manual(values=cbPalette)+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

## Controlling for analysis choices

>>>>

In a mature phono-lexical system, word recognition must balance flexibility to slight variation (e.g., speaker identity, accented speech) while distinguishing between phonological contrasts  that differentiate words in a given language (e.g. cat-hat). This meta-analysis examines the latter, focusing how infants apply the relevant phonological categories of their native language, aggregating twenty years' worth of studies using the mispronunciation sensitivity paradigm. The original study of @Swingley2000 presented American-English learning 18- to 23-month-olds with pairs of images of words they were very likely to know (e.g. a baby and a dog) and their eye movements to each image were recorded. Infants either heard the correct label (e.g. "baby") or a mispronounced label (e.g. "vaby") for one of the images. Although infants looked at the correct target image in response to both types of labels, correct labels elicited more looking to the target image than mispronounced labels. @Swingley2000 concluded that already before the second birthday, children's representations for familiar words are phonologically well specified. As we will review below, there are opposing theories and resulting predictions, supported by empirical data, as to how this knowledge is acquired and applied to lexical representations. The time is thus ripe to aggregate all publicly available evidence using a meta-analysis. In doing so, we can examine developmental trends making use of data from a much larger and diverse sample of infants than is possible in most single studies.

An *increase* in mispronunciation sensitivity with age is predicted by a maturation from holistic to more detailed phono-lexical representations and has been supported by several studies [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010]. The first words that infants learn are often not similar sounding [e.g. mama, ball, kitty; @CharlesLuce1995] and encoding representations for these words using fine phonological detail may not be necessary. According to PRIMIR [@Curtin2007; @Werker2005] infants' initially episodic representations give way to more abstract phonological word forms, as the infant learns more words, the detail of which can be accessed more or less easily depending on factors such as the infant's age or the demands of the task. This argument is supported by the results of @Mani2010kepstups, who found that 12-month-old infants with a larger vocabulary showed a greater sensitivity to vowel mispronunciations than infants with a smaller vocabulary.

@@

There are no theoretical accounts that would predict *decreased* mispronunciation sensitivity, but at least one study has found a decrease in sensitivity to small mispronunciations. Here, 18- but not 24-month-old infants showed sensitivity to more subtle mispronunciations that differed from the correct pronunciation by 1 phonological feature [@Mani2011]. @Mani2011 argue that when faced with large and salient mispronunciations, infants' sensitivity to small 1-feature mispronunciations may be obscured. This would especially be the case if infants show graded sensitivity to different degrees of mispronunciations (see below), as @Mani2011 found with 24- but not 18-month-olds in their study.

To disentangle the predictions that phono-lexical representations are progressively becoming more specified or are specified early, we investigate the relationship between mispronunciation sensitivity and age as well as vocabulary size. But, this may not account for all variability found in the literature. Indeed, different laboratories may vary in their approach to creating a mispronunciation sensitivity experiment, using different types of stimuli and methodologies. Many studies pose more nuanced questions, such as examining the impact of number of phonological features changed (mispronunciation size) or the location of the mispronunciation. Some studies may differ in their experimental design, presenting a distractor image that is either familiar or completely novel. In our meta-analysis we code for features of the experiment that are often reported but vary across studies and include an analysis of these features to shed further light on early phono-lexical representations and their maturation.

These research questions and experimental manipulations have the potential to create experimental tasks that are more or less difficult for the infant to successfully complete. The PRIMIR Framework [Processing Rich Information from Multidimensional Interactive Representations; @Curtin2007; @Werker2005] describes how infants acquire and organize the incoming speech signal into phonetic and indexical detail. The ability to access and use this detail, however, is governed by the task or developmental demands probed in a particular experiment. For example, if infants are tested on a more subtle mispronunciation that changes only one phonological feature, they may be less likely to identify the change in comparison to a mispronunciation that changes two or three phonological features [@White2008]. If older infants are more likely to be tested using a more demanding mispronunciation sensitivity task, this may attenuate developmental effects across studies. Note, however, that those studies reporting change [@Mani2007; @Altvater2014; @vanderFeest2015; @Altvater2010] or no change [@Swingley2000; @Bailey2002; @Zesiger2012] all presented the same task across ages.

The first set of questions concern how infants' sensitivity is modulated by different kinds of mispronunciations. Following on the above example, some experiments examine infants’ sensitivity to factors that change the identity of a word on a measurable level, or *mispronunciation size* (i.e. 1-feature, 2-features, 3-features), finding that infants are more sensitive to larger mispronunciations (3-feature-changes) than smaller mispronunciations (1-feature changes) for both consonant [@White2008; @Bernier2017; @Tamasi2016] and vowel [@Mani2011] mispronunciations, known as graded sensitivity. This also has consequences for understanding the developmental trajectory of mispronunciation sensitivity, as adults show similar graded sensitivity [@Bailey2005].

The position of mispronunciation in the word may differentially interrupt the infant’s word recognition process, but the degree to which position impacts word recognition is a matter of debate. The COHORT model [@Marslen-Wilson1989] describes lexical access in a linear direction, with the importance of each phoneme decreasing as its position comes later in the word. In contrast, the TRACE model [@McClelland1986] describes lexical access as constantly updating and reevaluating the incoming speech input in the search for the correct lexical entry, and therefore can recover from word onset and to a lesser extent medial mispronunciations. To evaluate these competing theories, studies often manipulate the *mispronunciation position*, whether onset, medial, or coda, in the word.

@@

A second set of questions is whether the experimental context modulates infants' responses to mispronunciations. In order to study the influence of mispronunciation position, many studies control the *phonological overlap between target and distractor labels*. For example, when examining sensitivity to a vowel mispronunciation of the target word "ball", the image of a ball would be paired with a distractor image that shares onset overlap, such as "bed". This ensures that infants cannot use the onset of the word to differentiate between the target and distractor images [@Mani2007]. Instead, infants must pay attention to the mispronounced phoneme in order to successfully detect the change.

@@

Mispronunciation sensitivity studies are typically examine infants' proportion of target looks (PTL) in comparison to some baseline measurement. PTL is calculated by dividing the percentage of looks to the target by the total percentage of looks to both the target and distractor images. Across papers the baseline comparison varied; since other options were not available to us, we used the baseline reported by the authors of each paper. Over half of the records (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post_naming_effect"])`) subtracted the PTL score for a pre-naming phase from the PTL score for a post-naming phase, resulting in a Difference Score. The Difference Score is one value, which is then compared with a chance value of 0. Pre vs. Post (*n* = `r with(dv_info, n_exp_conditions[within_measure == "pre_post"])` records) accomplishes the same analysis, directly compare the post- and pre-naming PTL scores with one another using a statistical test (e.g. t-test, ANOVA). This requires two values, one for the pre-naming phase and one for the post-naming phase. The remaining records used a Post dependent variable (*n* = `r with(dv_info, n_exp_conditions[within_measure == "post"])` records), which compares the post-naming PTL score with a chance value of 50%. Here, the infants' pre-naming phase baseline preferences are not considered and instead target fixations are evaluated based on the likelihood to fixate one of two pictures (50%). Standardized effect sizes based on mean differences, as calculated here, preserve the sign. Consequently, positive effect sizes reflect more looks to the target picture after naming, and larger positive effect sizes indicate comparatively more looks to the target.

@@

In the first analyses, we investigate the impact of age separately on conditions where words were either pronounced correctly or not. Age did not significantly modulate object identification in response to correctly pronounced (`r mod_test(rma_correct_age)`) or mispronounced words (`r mod_test(rma_MP_age)`). The lack of a significant modulation together with the small estimates for age (correct: $\beta$ `r full_estimate(Csum_eff)`; mispronunciation: $\beta$ `r full_estimate(Msum_eff)`) indicates that there was no relationship between age and target looks in response to a correctly pronounced or mispronounced label. However, previous experimental studies ([e.g. @Fernald1998]) and a recent meta-analysis [@Frank2016] have found that children's speed and accuracy in recognition of correctly pronounced words increases with age. Perhaps older children are more likely to be tested on less-frequent, later learned words than younger children, which could lead to a lack of a relationship between age and target looks in response to correct pronunciations in the current meta-analysis.

@@

```{r PlotMPEffect, echo = FALSE, fig.width=7,fig.height=7, fig.cap="Panel a: Effect sizes for correct pronunciations (orange) and mispronunciations (blue) by participant age. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) by participant age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

p <- ggplot(dat, aes(mean_age_1/30.44, g_calc, color = condition_label)) + 
  ggtitle("a. Object Recognition")+
  geom_point(aes(size = weights_g),show.legend=FALSE, alpha = .5) + 
  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
  #geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) +
  scale_colour_grey()+
  xlim(6, 31) +
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

p.diff <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity)) + 
  ggtitle("b. Mispronunciation Sensitivity")+
  geom_point(aes(size = weight),show.legend=FALSE, alpha = .3) + 
  geom_segment(aes(x = 6, y = 0, xend = 31, yend = 0), linetype="dotted", color = "black")+
  #geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1), color = "black") +
  scale_colour_grey()+
  xlim(6, 31) +
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

vocab_year <- ggplot(d.v,aes(x=Year, fill = relationship)) + 
  apatheme+
  geom_histogram(alpha = 0.5, bins = 20) +
    scale_fill_grey()+
     theme(legend.position = "bottom",
           legend.title = element_blank())

@@

#   
# 
# vocab_data1 <- dat.v %>%
#   group_by(year, relationship, tested) %>%
#   summarize(count = n())
# 
# vocab_data1 <- as.data.frame(vocab_data1)
# vocab_data1$count <- ifelse(vocab_data1$tested == "no", 0, vocab_data1$count)
# vocab_data1$year <- as.numeric(vocab_data1$year)
# 
# vocab_data1$relationship <- ifelse(vocab_data1$relationship == "no_vocab", "None",
#                                    ifelse(vocab_data1$relationship == "positive", "Predicts",
#                                           "No Relationship"))
# vocab_data1$relationship <- factor(vocab_data1$relationship, levels = c("Predicts", "No Relationship", "None"))
# 
# 
# p <- ggplot(vocab_data1, aes(year, count, color = relationship)) + 
#   geom_line() + 
#   geom_point()+
#   scale_y_continuous(breaks = c(0, 1, 2, 3, 4), limits = c(0,4))+
#   scale_colour_grey()+
#   apatheme +
#   theme(legend.title = element_blank(),
#         legend.position = "bottom")
# p
# 
#   jpeg(filename = "figures/Vocab_findings.jpg", 
#        width = 500, height = 300, units = "px")
# 
#   p
#   
#   dev.off()
#  
```

@@

If infants' word recognition skills are generally thought to improve with age and vocabulary size, research questions that tap more complex processes may be more likely to be investigated in older infants. In this section, we consider each moderator individually and investigate its influence on mispronunciation sensitivity. For most moderators (except mispronunciation size), we combine the correct and mispronounced datasets and include the moderator of condition, to study mispronunciation sensitivity as opposed to object recognition. To better understand the impact of these moderators on developmental change, we include age as subsequent moderator. Results of the 5 main moderator tests (mispronunciation size, mispronunciation  position, mispronunciation type, distractor overlap, distractor familiarity) as well as the individual effects for each moderator interaction are reported in Table 2. The statistic that tests whether a specific moderator explains a significant proportion of variance in the data, QM, was significant for all moderators and subsequent significant interactions of critical terms are interpreted. Finally, we analyze the relationship between infant age and the moderator condition they were tested in using Fisher's exact test, which is more appropriate for small sample sizes [@Fisher1922]. This evaluates the independence of infants' age group (divided into quartiles unless otherwise specified) and assignment to each type of condition in a particular moderator.

@@

To assess whether the size of the mispronunciation tested, as measured by the number of features changed, modulates mispronunciation sensitivity, we calculated the meta-analytic effect for object identification on a subset of the overall dataset, with `r with(nfeature_info, n_exp_conditions[n_feature == 0])` records for correct pronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 1])` for 1-feature mispronunciations, `r with(nfeature_info, n_exp_conditions[n_feature == 2])` for 2-feature mispronunciations, and `r with(nfeature_info, n_exp_conditions[n_feature == 3])` for 3-feature mispronunciations. Each feature change (from 0 to 3; 0 representing correct pronunciations) was considered to have an graded impact on mispronunciation sensitivity [@White2008; @Mani2011] and this moderator was coded as a continuous variable. We did not include records for which the number of features changed was not specified or consistent within a record (e.g., both 1- and 2-feature changes within one mispronunciation record).

@@

p.MS <- ggplot(dat.f, aes(Features_changed, g_calc, fill = Features_changed)) + 
  geom_violin() + 
  geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_grey()+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "none",
        axis.title.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Hedges' g")

@@

ms.age <- ggplot(dat.f, aes(mean_age_1/30.44, g_calc, color = Features_changed)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_grey()+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Hedges' g")

@@

```{r PlotMispPosit, echo = FALSE, fig.width=7,fig.height=3.5, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for mispronunciations on the onset, medial, and coda positions by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

ms.agg <- ggplot(dat.cm, aes(location_label, Misp_sensitivity, fill = location_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_grey()+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

@@

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = location_label)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_grey()+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

```{r PlotMispType, echo = FALSE, fig.width=10,fig.height=11, fig.cap="Panel a: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations. Panel b: Effect sizes for mispronunciation sensitivity within subject group and study (correct - mispronunciations) for consonant and vowel mispronunciations by age. For both panels, point size depicts inverse variance and the dashed line indicates zero (chance).", results="hide"}

@@

ms.agg <- ggplot(dat.cm, aes(type_label, Misp_sensitivity, fill = type_label)) + 
  #facet_grid(.~dv_label)+
    geom_violin() + 
    geom_boxplot(width=0.1)+
  #geom_jitter(height = 0, width = 0.1, alpha = 0.5)+
  labs(title="a")+
  #geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=weights_g)) + 
  scale_fill_grey()+
  apatheme +
  theme(text = element_text(size=25),
        legend.title = element_blank(),
        legend.position = "bottom",
        axis.title.x = element_blank(),
        axis.text.x = element_blank(),
        axis.ticks.x = element_blank()) + 
  #xlab("Number of Features Changed") + 
  geom_hline(yintercept = 0, linetype="dotted") + 
  ylab("Misp. Sensitivity")

ms.age <- ggplot(dat.cm, aes(mean_age_1/30.44, Misp_sensitivity, color = type_label)) + 
    #facet_grid(.~dv_label)+
  geom_point(aes(size = n_1),show.legend=FALSE) +
  labs(title="b")+
  geom_line(y= 0, linetype="dotted") + 
  geom_smooth(method = "lm", formula = y ~ log(x), aes(weight=n_1)) +
  scale_colour_grey()+
  apatheme +
  theme(legend.title = element_blank(),
        legend.position = "bottom") + 
  xlab("Age in months") + 
  ylab("Misp. Sensitivity")

@@

## Controlling for analysis choices and re-running the main meta-analytic models
